Kindly Bent to Free Us

### 2019-06-28 kindly/motivation.tex
make the array example a bit more liberal.

\begin{figure}
  \centering
  \begin{subfigure}{0.48\linewidth}
\begin{lstlisting}
module Array : sig
  type ('a : un) t : aff

@@

  val get : &('a t) * int -> 'a
  val set : &!('a t) * int * 'a -> unit
end
\end{lstlisting}
    \caption{Affine primitives}
    \label{sig:array}
  \end{subfigure}\hfill
  \begin{subfigure}{0.5\linewidth}
\begin{lstlisting}
let mk_fib_array n =
  let a = create n 1 in
  for i = 2 to n - 1 do
    let x = get &a (i-1) + get &a (i-2) in(*@\label{ex:array:get}*)
    set &!a i x(*@\label{ex:array:set}*)
  done;
  a(*@\label{ex:array:return}*)
# mk_fib_array : int -> int Array.t
\end{lstlisting}
    \caption{Example of use of affine arrays}
    \label{ex:array}
  \end{subfigure}
\end{figure}

>>>>

\begin{figure}
  \centering
  \begin{subfigure}{0.48\linewidth}
\begin{lstlisting}
module Array : sig
  type ('a : 'k) t : 'k

@@

  val get : ('a : un) => &('a t) * int -> 'a
  val set : &!('a t) * int * 'a -> unit

  val map : (&'a -> 'b) -> &('a t) -> 'b t
end
\end{lstlisting}
    \caption{Affine arrays}
    \label{sig:array}
  \end{subfigure}\hfill
  \begin{subfigure}{0.5\linewidth}
\begin{lstlisting}
let mk_fib_array n =
  let a = create n 1 in
  for i = 2 to n - 1 do
    let x = get (&a, i-1) + get (&a, i-2) in(*@\label{ex:array:get}*)
    set (&!a, i, x)(*@\label{ex:array:set}*)
  done;
  a(*@\label{ex:array:return}*)
# mk_fib_array : int -> int Array.t
\end{lstlisting}
    \caption{Example of use of affine arrays}
    \label{ex:array}
  \end{subfigure}
\end{figure}
